Deep Learning for 3D Brain Activity Scans

### 2019-12-02 paper/submission.tex
Adding saliency, some more visualizations
Working on f1scores from trained model

@@

>>>>

11171266 trainable params in resnet18 2d
33148482 trainable params in resnet18 3d (about 2.97x)

data size tho -
30x bigger (30 x 44 x 40) vs (44 x 40)

Future works
- could strive to refine 3d more, with more time and compute
- unsupervised segmentation would be cool
- find ways to not have to smoosh images for memory?
- more visualizations? lack of color kinda sucks, saliency is weird, filters prob too

ACTUAL FINAL WORK
- check out filter viz
- see about unsupervised
- try 3d alternative archs? (dont really need to)
- "none of my alterations to the model architecture worked that well, most did nothing, a few broke things, could still poke around more though"
- better assessment metrics (f1s, auc)

@@

              nonfood        food
precision    0.893162    0.935323
recall       0.941441    0.882629
f1           0.916667    0.908213
support    222.000000  213.000000
